\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-20 WOOT/Files/related_work.tex
remove of mode comparison, fix effective table

~\ref{table:ccc}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}

@@

		\hline 
		USB condom \cite{Condom}& yes & yes & yes & yes & yes\\
		\hline 
		Pham et al. \cite{pham2010optimizing}, odix\cite{OLEA}& no & ? & no & no & no\\
		\hline 
		TMSUI\cite{yang2015tmsui}& no & yes? & no & no & no\\
		\hline 
		Windows Defender ATP\cite{windenfenderwhite}& no & yes? & no & no & no\\
		\hline 
		GoodUSB\cite{tian2015defending}& yes & yes & yes? & no & no \\

		\hline
		Neuner et al.\cite{neuner2018usblock}& yes & no & no & no & depends? \\
		\hline
		Meng et al\cite{meng2018252}& no & no & yes & no & ?\\
		\hline
	\end{tabular}
	\linebreak
	\caption{Effectiveness of defense against different attacks}
	\label{table:ccc}
\end{table*}

>>>>

We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrated the effectiveness of each defense against various attacks including our \tool.
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}

@@

		\hline 
		USB condom \cite{Condom}& Yes & Yes & Yes & Yes & Yes\\
		\hline 
		Pham et al. \cite{pham2010optimizing}, odix\cite{OLEA}& No & ? & No & No & No\\
		\hline 
		TMSUI\cite{yang2015tmsui}& No & Yes? & No & No & No\\
		\hline 
		Windows Defender ATP\cite{windenfenderwhite}& No & Yes? & No & No & No\\
		\hline 
		GoodUSB\cite{tian2015defending}& Yes & Yes & Yes? & No & No \\

		\hline
		Neuner et al.\cite{neuner2018usblock}& Yes & No & No & No & depends? \\
		\hline
		Meng et al\cite{meng2018252}& No & No & Yes & No & ?\\
		\hline
	\end{tabular}
	\linebreak
	\caption{Effectiveness of defense against different attacks}
	\label{table:attack_vs_defense}
\end{table*}
